I/O simulation extension for SimGrid framework

### 2020-04-22 paper_io_sim.tex
Add references

	\section{Introduction}
		\begin{itemize}
			\item HPC, the bottleneck in I/O and the demand of HPC experiments. 
			\item Difficulties in conducting high performance computing experiments and the need of simulation frameworks.
			\item Existing experiment methods, simulators, simulation frameworks. The advantages of SimGrid compared to others. The missing of the ability to simulate page cache in SimGrid.
			\item The objective of the paper: Add capability to simulate I/O with page cache in SimGrid.
		\end{itemize}
	\section{Related Work}

		\subsection{Page cache}
			\begin{itemize}
				\item What is page cache? How it works. Effects and importance of page cache.
				\item Introduce some existing strategies with some highlighted pros and cons.
				\item Current implementation in Linux and some reasons why it is chosen to be implemented (implementation complexity, effectiveness, overhead, etc)
			\end{itemize}

@@

>>>>

	\section{Introduction}
		\begin{itemize}
			\item HPC, the bottleneck in I/O and the demand of HPC experiments. 
			\item Difficulties in conducting high performance computing experiments and the need of simulation frameworks.
			\item Existing experiment methods, simulators, simulation frameworks. The advantages of SimGrid compared to others \cite{casanova2008, lebre2015}. The missing of the ability to simulate page cache in SimGrid \cite{lebre2015}.
			\item The objective of the paper: Add capability to simulate I/O with page cache in SimGrid.
		\end{itemize}
	\section{Related Work}

		\subsection{Page cache}
			\begin{itemize}
				\item What is page cache? How it works \cite{linuxdev3rd2010}. Effects and importance of page cache.
				\item Introduce some existing strategies with some highlighted pros and cons.
				\item Current implementation in Linux and some reasons why it is chosen to be implemented (implementation complexity, effectiveness, overhead, etc) \cite{linuxdev3rd2010}
			\end{itemize}

@@

\bibliographystyle{plain}
\bibliography{citation}
